Untitled

### 2017-07-19 PaperCode.Rmd
Remove ANOVA
the anova doesn't work when only A is used doe to the class bounardies. It is n't very interesting anyway so I removed it from the function

@@

@@

#Norfolk
```{r}
#Broadlands is unsuable, due to lack of data collection.
#This is being checked
# BroadlandsDATA <- read_excel("BroadlandDiscountsLSOA.xlsx", sheet=1)[1:4] %>%
#   StructureData()

@@

@@

BrightonDATA <- read_excel("Copy of Brighton and HoveDiscountsLSOA (4).xlsx", sheet=1)%>% .[,c(2,3:5)] %>%
  StructureData(lowuse = 2:8)

#MakeLeaflet(BrightonDATA)

@@

@@

@@

CarmarthenDATA <- read_excel("CarmarthenshireDiscountsLSOA.XLSX" , sheet=1)%>% .[,1:4] %>%
  StructureData(2:4)

@@

z<- MakeLeaflet(MonmouthDATA)
z
# 
# saveWidget(z, file=file.path(basewd, "CeredigionDATA"), selfcontained = TRUE )

#testSouth <- DistribCompareBootstrapper(SouthwarkLONDATA, 1652, 1000)
testSouth %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100) %>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

@@

#Inlcude only transfers and Buy-to-let and purcheses to non-private individuals
BootStrapRESA <-LoadAddDistribCompare("BootStrapRES_B.rds", type = "B")

@@

@@

CeredPrice <- prices %>% 
  filter( grepl("W06000008", Admin_district_code)) %>%
  select(Admin_ward_code, lsoa11cd, Price =X2, X15) %>%
  #filter(X15 == "A") %>%
  mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
                     labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
                     right = F),
         Price = as.numeric(Price))

@@

CeredBootAnorm <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, type = "A" )
CeredBootAB <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, c(0, 60, 120, 200, 500, Inf)*10^3 )

CeredBootA <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, c(0, 60, 120, 200, 500, Inf)*10^3, type = "A" )

@@

CeredBootAB %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

CeredBootA %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

CeredBootAnorm %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

@@

@@

#This is so cool, Also needs to be discussed in great detail, it is probablu due to the demolition and renovation of council housing
Combine1 %>% ggplot(.,aes(x= absdiff, y = Ttest.p.value)) + geom_point()

@@

@@

@@

>>>>

#Devon

NorthDevonDATA <- read_excel("North DevonDiscountsLSOA.XLSX", sheet=1)[1:4] %>%
  StructureData

#Somerset

```{r}
NorthSomsertDATA <- read_excel("1501796 North SomersetDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
  StructureData(lowuse= 2:6)

#Dorset

```{r}
BournemouthDATA <- read_excel("Copy of FOI - 265 - Bourne - PooleDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
  StructureData(lowuse = c(5,11:14,18))
```

@@

StEdmundsDATA <- read.xlsx("se FOI 146  3948502_Copy+of+St+EdmundsburyDiscountsLSOA.xlsx")[1:4] %>%
  StructureData()

ForestHeathDATA <- read.xlsx("FH FOI 146 Discounts.xlsx")[1:4] %>%
  StructureData()

@@

#Norfolk
```{r}
#Broadlands is unsuable, due to lack of data collection.
#This is being checked
BroadlandsDATA <- read_excel("BroadlandDiscountsLSOA.xlsx", sheet=1)[1:4] %>%
  StructureData(4:9)

KingsLynnDATA <- read_excel("197782 - King s Lynn and West NorfolkDiscountsLSOA (2).xlsx" , sheet=1)[1:4] %>%
  StructureData(2:11)

NorthNorfolkDATA <- read_excel("North NorfolkDiscountsLSOA.XLSX" , sheet=1)[1:4] %>%
  StructureData()

@@

FenlandDATA <- read_excel("FL FOI 4544 DISCOUNTS.XLSX" , sheet=1)[1:4] %>%
  StructureData()

@@

BrightonDATA <- read_excel("Copy of Brighton and HoveDiscountsLSOA (4).xlsx", sheet=1)%>% .[,c(2,3:5)] %>%
  StructureData(lowuse = 2:8)
#MakeLeaflet(BournemouthDATA)

@@

#Selby
SelbyDATA <-read_excel("SelbyExemptionsLSOA.xlsx" )[,1:4]%>%
  StructureData(20:27)

@@

#Ceredigion completed some major Student Halls which were transferred to the University, this created some very large B type transfers which artificially push the cost of second homes lower than the price of regular homes.

@@

#includes the zero class which is descibeed as 
#ZERO – tis is a 50% reduction which applies after exemptions that are time limited, have expired. They are awarded on the basis that the property remains unoccupied and unfurnished.
  CarmarthenDATA <- read_excel("CarmarthenshireDiscountsLSOA.XLSX" , sheet=1)%>% .[,1:4] %>%
    StructureData()

@@

z<- MakeLeaflet(CeredigionDATA)
z
# 
setwd(basewd)
 saveWidget(z, file=file.path(basewd, "CeredigionDATA.html"), selfcontained = TRUE )

#testSouth <- DistribCompareBootstrapper(SouthwarkLONDAls(pattern = "DATA")TA, 1652, 1000)
testSouth %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100) %>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

@@

#Inlcude only transfers and Buy-to-let and purcheses to non-private individuals
BootStrapRESB <-LoadAddDistribCompare("BootStrapRES_B.rds", type = "B")

@@

ls(pattern = "DATA")[(ls(pattern = "DATA") %>% map_dbl(~get(.x) %>%ncol))==4]

@@

CeredPrice <- prices %>% 
  filter( grepl("E09000001", Admin_district_code)) %>%
  select(Admin_ward_code, lsoa11cd, Price =X2, X15) %>%
  #filter(X15 == "A") %>%
  mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
                     labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
                     right = F),
         Price = as.numeric(Price))

@@

# CeredBootAnorm <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, type = "A" )
# CeredBootAB <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, c(0, 60, 120, 200, 500, Inf)*10^3 )
# 
# CeredBootA <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, c(0, 60, 120, 200, 500, Inf)*10^3, type = "A" )

@@

BootStrapRES$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

BootStrapRESA$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

BootStrapRESB$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

@@

#check any that are accidently not processed
ls(pattern = "DATA")[(ls(pattern = "DATA") %>% map_dbl(~.x %>% get %>% ncol))<10]

@@

Combine2 <- BootResSummaryData(BootStrapRESA)

Combine3 <- BootResSummaryData(BootStrapRESB)

#This is so cool, Also needs to be discussed in great detail, it is probablu due to the demolition and renovation of council housing
Combine1 %>% ggplot(.,aes(x= absdiff, y = Ttest.p.value)) + geom_point()
Combine2 %>% ggplot(.,aes(x= absdiff, y = Ttest.p.value)) + geom_point()

@@

BootStrapRES$ChelseaLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

BootStrapRESA$ChelseaLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

BootStrapRESB$ChelseaLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

BootStrapRES$CoLLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

BootStrapRESA$CoLLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

BootStrapRESB$CoLLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

@@

sum(Combine1$Ttest.p.value>0.5)/nrow(Combine1)
sum(Combine1$Ttest.p.value>0.5 & Combine1$maxPerc>5)/sum(Combine1$maxPerc>5)

Combine1[Combine1$Ttest.p.value>0.5 & Combine1$maxPerc>5,]
Combine2[Combine2$Ttest.p.value>0.5 & Combine2$maxPerc>5,]
Combine3[Combine3$Ttest.p.value>0.5 & Combine3$maxPerc>5,]

table(Combine2$Ttest.p.value>0.5 & Combine2$maxPerc>5, Combine1$Ttest.p.value>0.5 & Combine1$maxPerc>5)

LADAB <- ChelseaLONDATA%>% SubsetPrice
  table(LADAB$X15, LADAB$class)

@@

Combine2 %>% ggplot(.,aes(x= maxPerc, y = Ttest.p.value)) + geom_point() +
  labs(title = "Comparing tatistical Significance of LUPs being more expensive than RHs and the maximum concentration of LUPs in a ")
